---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->
<!-- badges: start -->
[![R-CMD-check](https://github.com/jhuwit/actisleep/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/jhuwit/actisleep/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/jhuwit/actisleep/branch/main/graph/badge.svg)](https://app.codecov.io/gh/jhuwit/actisleep?branch=main)
<!-- badges: end -->
    
```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  cache = TRUE
)
```

# actisleep

`actisleep` provides helpers for sleep estimation from actigraphy.

Core entry points:

- `calculate_measures()` for summary metrics such as AI, MAD, MIMS, and AC
- `acti_calculate_counts()` and `acti_process()` for count and wear overlays
- `mims_default_processing()` for the default MIMS preprocessing chain
- `acti_calibrate()` for calibration through `agcounts` using the van Hees
  method commonly implemented in `GGIR`

## Installation

You can install `actisleep` from GitHub with:

```{r gh-installation, eval = FALSE}
# install.packages("remotes")
remotes::install_github("jhuwit/actisleep")
```

## Quick Start

```{r example}
library(actibase)
library(actiread)
library(actisleep)
path <- actiread::acti_example_gt3x()
data <- actiread::acti_read_gt3x(path, verbose = FALSE)
```

